Title

### 2014-07-22 paper.tex
add some scatter plot

% corpus size and other statistics

\subsection{Studied Project and Data set}
\subsection{RQ1: Can we identify useful and useless discussion in code review?}
\subsection{RQ2: How impact of useless discussion impact to the software quality?}

>>>>

After the similarity and distance metrics have been calculated,
these metrics appear to be able to separate the useful comments from the non-useful ones,
as can be seen in Fig.\ref{fig:scatter}.
Note that many comments have a cosine similarity metric of 0.
This is because the comment text and the corresponding commit message has no word in comment.

\begin{figure}[h]
\centering
\includegraphics[width=3in]{scatter}
\caption{The similarity and distance plot of the training data.
The symbol represents the score, which ranges from 0 to 3.}
\label{fig:scatter}
\end{figure}

From our training data,
the following criteria have been found:

For ``yes'' result:
\begin{gather*} similarity \geq 0.015528969196702956 \text{ and}\\ distance \leq 2.4949438168165483 \end{gather*}

For ``no'' result:
\begin{gather*} similarity \leq 0.08752176628812282 \text{ and}\\ distance \geq 2.26567908457803 \end{gather*}
